\Large \bf Dynamic Program Dialysis with Lya

### 2020-01-14 paper/draft.tex

\newcommand{\R}{\ttt{R}\xspace}
\newcommand{\W}{\ttt{W}\xspace}
\newcommand{\X}{\ttt{X}\xspace}
\newcommand{\E}{\ttt{X}\xspace}
\newcommand{\rwx}{\ttt{RWX}\xspace}

@@

%for single author (just remove % characters)
\author{
{\rm Anonymous Author(s)}\\
\normalsize{Submission \#225, 11 + 2 pages}\\
% \normalsize{Additional Anonymized Material: \href{https://git.io/JvfCf}{https://git.io/JvfCf}.}
% {\rm Grigoris Ntousakis}\\
% Technical University of Crete
% \and
% {\rm Nikos Vasilakis}\\
% Massachusetts Institute of Technology
}

@@

To address these challenges, we propose a novel approach to dynamic analysis, termed \emph{dialysis}\footnote{
  A method of deconstruction into elements often for the purposes of removing waste products or altering piecewise components.
  From ancient Greek {\scriptsize $\delta\iota\acute{\alpha}$} (di\'{a}, ``inter-, through'') and {\scriptsize $\lambda\acute{\tilde{\upsilon}}\epsilon\iota\nu$} (lúein, ``to loosen'').
} and implemented in \sys.
Program dialysis is a general technique, applicable to any programming language, that enables dynamic fragmentation, analysis, and reassembly of applications at the level of individual libraries. 
It operates during program execution, automating wrapping and transformation of the program's dependency graph, and allowing developers to extract meaningful insights with only a few lines of analysis-specific code
By operating at the granularity of libraries, dialysis has several benefits over prior work: %full-fledged dynamic analysis:
  (i) it allows bolting library dialysis itself as a library onto existing runtime environments with no dynamic analysis,
  (ii) it supports analysis expressions using the same language, tools, and abstractions as the host program language,
  (iii) it features significantly low runtime performance overheads, enabling the potential for toggling its use in production environments.

@@

To demonstrate its effectiveness, we evaluate \sys on the JavaScript ecosystem (>1.2M libraries~\cite{modulecounts}). % and unusually high code-reuse~\cite{npmstudy:19}. %, and a pressing need for usable dynamic analysis~\cite{}.
We develop a diverse set of analyses that target practical information about a program:
  an allow/deny security analysis,
  a profiling analysis showing bottlenecked modules,
% a synthesis-oriented analysis on input-output data,
  and an analysis extracting union-based type invariants.
This set of analyses drives the design requirements for \sys, and highlights dialysis as a middle ground between coarse- and fine-grained analysis.
We evaluate \sys at three different levels:
  (i) synthetic micro-benchmarks that test certain aspects and confirm the correctness of our analyses in a controlled environment;
  (ii) single-module meso-benchmarks that allow comparison with dynamic analysis frameworks; and
  (iii) end-to-end full-application macro-benchmarks that show behavior of \sys on realistic workloads. 
\S\ref{bg}--\ref{eval} present our key contributions:
\begin{itemize}
\item \S\ref{bg} characterizes the shared needs of three case-study multi-module analyses whose needs remain mostly unmet by general-purpose analysis frameworks.
\item \S\ref{design} presents the design of the bolt-on module-oriented dynamic analysis~\sx{design}, which meets the requirements of the three case-study analyses.
\item \S\ref{impl} discusses our implementation, \sys, as a pluggable library for the JavaScript ecosystem, as well as the implementation of the three analyses.
\item \S\ref{eval} evaluates \sys showing it expresses insightful analyses succinctly, adds minimal overheads over the baseline runtime, and scales to hundreds of modules.
\end{itemize}

@@

A single application today often incorporates multiple libraries written and published by several different authors.
To make the difficulties of analyzing such library-overreliant software more concrete, we describe three example analyses~\sx{examples}.
These examples illustrate key requirements for the design of a framework for analyzing applications at the boundaries of modules~\sx{goals}.
Before describing these examples, however, we offer a brief refresher on the %abstractions and corresponding
  internals of module systems~\sx{bg1}.

@@

\begin{figure}[t]
\raggedleft 
\includegraphics[width=0.45\textwidth]{./figs/lya_ex1.pdf}
\caption{
  \textbf{Example of a library import.}
  \textmd{
    The program on the left imports the \ttt{simple-math} library, shown right, which imports \ttt{log} and exports a \ttt{Math} object.
    Several names are provided by the programming language:
      \ttt{import} and \ttt{exports} resolve to library-local values; \ttt{print} resolves to a global value.
  }
  \vspace{-8mm}
}
\label{fig:ex1}
\end{figure}

A library, package, or module---we use these terms interchangeably---is a development-time construct encapsulating reusable functionality.
This functionality falls into two categories:
  it either (i) comes bundled with the language, possibly wrapping operating-system interfaces, such as the file-system, in a way that is system-agnostic and conforms to the language's conventions,
  or (ii) provided by other developers sharing code others might find useful.
Fig.~\ref{fig:ex1} shows a \ttt{simple-math} library (right) imported by a program (left).

From a developer's perspective, \ttt{import}ing a library makes its functionality available to the calling code by means of binding its functionality to a name in the caller's scope.
% What this means is that some of the library's functionality is bound to a variable name that becomes available in the scope of the caller.
This is achieved by some form of \ttt{export}ing, where the library developer expresses which values should become available to the \ttt{import}ing code.
The definition of a value depends on the semantics of the language; for now we can assume it's either a primitive value, a list of values, a function, or an object mapping string keys to values.
Internally, the library may \ttt{import} other libraries, cause side-effects to the file-system or the network, or even be implemented in multiple languages.
% , as shown on line \fixme{XX},
% closely coupled with the runtime
% and in some cases features its own mini-language, as is the case in Scheme and Standard ML.

From the programming language's perspective, the process of \ttt{import}ing a library is achieved in several steps. 
Compiled languages support separate compilation, where source files are compiled individually, followed by a runtime-linking phase that loads and links the resulting object files.
Interpreted languages involve a somewhat convoluted process that combines runtime loading, interpretation, and linking.
This process starts by locating the library in the file system % or across the network,\footnote{
%   Examples of run-time environments featuring network loading include V8 and deno, for executing JavaScript and TypeScript respectively.
% }
by resolving relative or absolute identifiers.
% The library is assigned a unique identifier.
The content of the library is then read and wrapped in a way that resolves library-local names such as \ttt{\_\_name\_\_} in Python and \ttt{\_\_filename} in JavaScript to meaningful values.
The wrapper is then interpreted and evaluated using the language's interpreter, which might result to side-effects---for example, a \ttt{process.exit()} in the library's top-level scope will exit the entire program.
Finally, the value bound to the \ttt{export}ed interface or returned from this interpretation (depending on the language) is made available to the scope of the  \ttt{import}ing code.

There is significant variation, but a few features are common across many implementations.
A library cache maintains a mapping from library identifiers, often absolute paths, to returned \ttt{export} values.
The cache serves a dual purpose:
  by avoiding locating already loaded libraries, it improves performance and ensures the consistency of any library-internal state.
Recursive imports are handled in a depth-first way, and when cyclical dependencies are possible they are resolved by pointing to the cache.
An increasingly common feature is to allow different versions of the same library to co-exist in a program, in order to avoid a choice between mutually exclusive options---a paradoxical situation known as ``dependency hell''.
As a result, a single \ttt{import} \ttt{l} does not necessarily resolve to the same (version of the) library \ttt{l} every time.
The dual of this is also possible: two different library names may resolve to the same identifier (in which case the second will be redirected to the cache).
These features complicate library-level analysis, especially in interpreted programming languages.

@@

\subsection{Motivating Examples}
\label{examples}

Having reviewed the building blocks and underlying techniques that power modularity, we now turn to examples of dynamic analysis that today are difficult or require specialized solutions:
  (i) an allow/deny security analysis,
  (ii) a performance-profiling analysis showing bottlenecked libraries, and
% (iii) a synthesis-oriented analysis on input-output data, and
  (iii) an analysis extracting runtime type invariants.
These examples illuminate key design requirements for \sys's implementation of module-level dynamic analysis.

\heading{Security Analysis}
The pervasive reliance on third-party libraries has led to an explosion of supply-chain attacks~\cite{long2015owasp, maass2016theory, snyk, lauinger2017thou}.
Both bugs and malicious code in libraries create attack vectors, exploitable long after libraries reach their end-users.
As library boundaries disappear at runtime, libraries end up executing with no meaningful isolation or privilege separation guarantees between each other and the trusted portions of a program.
Popular libraries, depended upon by tens of thousands of other libraries or applications, allow vulnerabilities deep in the dependency graph to affect a great number of applications~\cite{leftpad, npmstudy:19}.
Discovered vulnerabilities are becoming harder to eradicate, as updates are fetched automatically~\cite{npmFailure} and module unpublishing is becoming a multi-step process to avoid breaking applications~\cite{npmUnpublish}.
Worst of all, leaked publishing tokens allow attackers to update packages with code that will eventually reach end-users via package updates~\cite{eslint1}.

As a concrete example, consider the recent \ttt{event-stream} incident~\cite{es1, es2}, in which a maintainer of a highly popular library inserted code stealing Bitcoin wallet credentials from programs using that library.
Heavy-weight, offline dynamic analysis~\cite{jalangi} would not have helped, as \ttt{event-stream} activated only on production (rather than testing or development).
Coarse-grained analysis at program boundaries, say via containment or system-call interposition~\cite{systrace:03}, would have not helped either because host programs already used the network and disk.
Finally, static analysis would have been of little use, as \ttt{event-stream} encrypted its source code.

Having the ability to toggle a library-level ``allow-deny'' security analysis on/off at runtime would have revealed the (unusual) resources touched by \ttt{event-stream}.
Analyzing the behavior \emph{within} the library itself is not critical:
  if any data exfiltration is happening, it will require calling out of the library and into the network---in \ttt{event-stream}'s case, using the \ttt{fs} library to modify a different library and then use \ttt{http} from the second library.
Both \ttt{fs} and \ttt{http} are part of the standard library, built into the runtime environment.
Examples of interfaces outside the \ttt{http} and \ttt{fs} libraries include the ability to use global variables, import other libraries, and access the cache of the loaded modules---all of which are unfortunately available to any third-party that is part of an application.
% The key issue underlying the \ttt{event-stream} attack is that any third-party fragment of an application has unrestricted access to the functionality available to the rest of application.

 %% To address such problems, several recent proposals suggest analyzing third-party modules dynamically to identify malicious behavior~\cite{}.
 %% % FIXME more about the policy, tracking arguments too
 %%  indicating the resources touched by that library 
 %% it seems critical to be able to toggle analysis on/off on production.
% \emph{
% This case highlights the need to \fixme{analyze} all the observable behavior \emph{around} a library, without necessarily caring about fine-grained library-internal analysis.
% }

\heading{Performance Diagnosis}
Diagnosing performance problems is a difficult task, exacerbated by the heavy use of third-party libraries.
Libraries are written by authors with different education, backgrounds, quality standards, and, most importantly, needs:
  it is not unusual for a weekend project solving a local need to end up as a critical dependency among several open-source projects~\cite{cheapcomplexity}.
Maintenance and rewriting can also cause performance regressions between two versions of a library;
% FIXME: Garbage collection
  worse even, the fact that a library changes one of its dependencies can cause severe performance pathologies to upstream projects---that is, while an interface remains the same due to an intermediate layer of abstraction, its performance can change dramatically~\cite{jest}.

As a concrete example, consider the \ttt{minimatch} library, a regular-expression-based file-matching utility susceptible to long delays due to regular expressions that involve backtracking~\cite{minimatch}.
Pathological inputs reaching \ttt{minimatch}, even if benign, can cause significant performance degradation~\cite{redos} deep in the dependency chain, affecting also other parts of the program competing for the same resources~\cite{evp}.
Developers use various techniques to understand such problems---\eg collecting and replaying traces against off-line versions of the system, or using statistical profiling to identify hot code-paths.
These techniques, however, require significant \emph{manual} effort:
  capturing traces, setting up test-beds, replaying traces, analyzing statistics, and debugging performance are all tedious and time-consuming tasks, compounded by the difficulties of mapping the results to the right third-party libraries.

Switching on a library-level profiling analysis % that operates at library boundaries
  would quickly detect a slowdown and attribute it to the bottlenecked \ttt{minimatch}.
Wrapping library interfaces with profiling logic would collectively construct a model of the current workload.
Such profiling could operate at a high resolution in time and space---at every function call entering a library and on hundreds of libraries across an application---but does not need to track detailed operations such as direct variable accesses.
% An analysis could treat library invocation boundaries as message queues~\cite{scheme:98, duality:79} growing when a library gets overwhelmed.
% At some point, the waiting time of newly-arrived messages becomes longer than sending messages to a library replica.
Each library wrapper can collect profiling statistics at its own boundary, aggregating summaries into a global structure ordering libraries by resource consumption.

@@

\heading{Type Invariant Discovery}
Extracting type information in a program is helpful in a variety of different ways. %, as type safety is an important property helpful in variety of scenarios. 
%and types are lightweight annotations that can be quickly and efficiently checked.
For example, types can be used to (i) identify program invariants to be preserved during code modifications, (ii) generate (machine-checkable) program documentation, or (iii) guide program synthesis and regeneration~\cite{daikon}.
This is especially important in dynamic programming languages:
  in the absence of static type signatures, there is not much one can say about an object without executing it and inspecting its properties.

As a case in point, consider the \ttt{gRPC} library for serializing and de-serializing objects~\cite{grpc}.
To use it, developers have to provide a protocol-buffer specification describing the types of values that will be serialized.
Given a library---say, bignum or crypto---a developer has to first call it manually, take note of the result's type, and then fill in the protobuf spec. %, common in distributed systems
This process has to be repeated with every change, often due to library updates or changes in the consuming program's structure.

Dynamic analysis can be used to discover such type assertions or invariants.
The analysis would consult the (static) definition of a type \emph{system}, capturing the type of values at the library boundaries by observing the execution of the program.
%% TODO: such as the simply-typed lambda calculus augmented with objects and union types.

@@

\subsection{Design Goals}
\label{goals}

We have briefly introduced three motivating analyses for extracting information about an application's dependencies.
While the challenges behind these analyses share several characteristics, today they remain largely unaddressed by dynamic analyses frameworks due to a combination of factors:
  these frameworks either require highly specialized solutions often outside the core language,
  do not leverage or offer semantic information at the level of library boundaries, or
  lead to a high (often impractical) performance overheads due to the high granularity of their analyses.
To summarize, these applications would appear to be served well by a system that:
\begin{itemize}
  \item \textbf{(G1)} Operates at the level of libraries, leveraging both the semantics and performance potential that this level of granularity can potentially offer.
  \item \textbf{(G2)} Does not require learning a new tool or language, but rather allows developers to express their analyses in the same language as the program.
  \item \textbf{(G3)} Can be implemented as a library that bolts analyses onto an existing language runtime environment.
% \item \textbf{(G4)} It does not incur prohibitive overheads, such that it can be switched on and off selectively during runtime execution.
\end{itemize}

The next section describes program dialysis, a new analysis technique that satisfies these goals, in a language-agnostic manner~\sx{design};
  the section following that describes a concrete implementation for the server-side JavaScript ecosystem~\sx{impl}.

@@

% FIXME: add user data
Program dialysis operates by
  dismantling the program at the boundaries of libraries,
  applying transformations that insert analysis-specific machinery, and then carefully 
  reassembling individual components to maintain the original semantics:

@@

  \item \textbf{Dismantling:}
Dialysis starts by recursively dismantling a program into its dependencies. % ---pieces of software implement a computation or functionality.
This is achieved by re-wiring the language's \ttt{import} function to go through \sys, resulting in \sys walking the program's recursive dependency structure at runtime.
During this phase, \sys has to determine the granularity of the analysis (\eg top-level libraries, a specific library \etc) in order to apply transformations at the correct level and map th provided analysis hooks to the corresponding libraries.

@@

  \item \textbf{Reassembly}
Finally, dialysis reassembles individual modified libraries back into the program's original structure.
The most important challenge during this phase is the treatment of the library cache~\sx{bg1}.
The cache needs to be augmented to support multiple wrappers per library, each capturing a small fragment of the overall analysis.
% without breaking the program's semantics.
% ensure every fragment finds its place during dependency reassembly,

@@

\begin{figure}[t]
\raggedleft 
\includegraphics[width=0.45\textwidth]{./figs/lya_base.pdf}
\caption{
  \textbf{Base transformation.}
  \textmd{
  The algorithm (simplified) is presented in functional style to simplify variable binding; types (object, list, function, and primitive), used for pattern matching, are shown in light {\color{cdb} \emph{turquoise}}~\cf{two}. The functions $\alpha_1$, $\alpha_2$, and $\alpha_3$ stand for the locations of analysis hooks.
  }
  \vspace{-4mm}
}
\label{fig:base}
\end{figure}

@@

When a dialysis-augmented program starts, it first loads the analysis file provided by the developer. 
The file may specify a subset of libraries whose boundaries are of interest or a subset of libraries that should \emph{not} be analyzed.
Among other things, \sys needs to determine the library boundaries of interest and the granularity of analysis.
To do this, it extracts a static approximation of the dependency graph by traversing library files.
Using this graph, it processes the analysis file to extract a mapping from library identifiers to analysis hooks.
It also checks for constructs not associated with libraries---for example, whether the analysis includes global variables, library-local constructs, standard libraries \etc
\sys then proceeds to dynamically replace the implementation of \ttt{import} and launch the program:
  rather than simply locating and loading a library, calls to \ttt{import} now yield to \sys.

For every invocation of \ttt{import} \sys checks the cache~\sx{three} to determine
  (i) if the library has already been loaded, and
  (ii) whether it has been loaded with the same analysis hooks.
If both are determined true, \sys retrieves the cached version of the library and returns the transformed \ttt{export}ed value.
If the library was loaded with a different analysis---say because there are different analyses applied to different parts of a dependency tree---\sys constructs the appropriate analysis and applies a transformation pass on a cached copy of the unmodified library~\sx{three}.
% \omit{---the common case---}
Otherwise, \sys first invokes the built-in library loader to locate the library.

The process of loading new libraries includes (i) a phase of reading the necessary source files and (ii) a phase of interpreting them, interspersed by applications of transformations~\sx{two}.
Reading files returns a string representation of the code; interpretation uses the language's runtime evaluation primitives to convert the code into an in-memory object.
% A series of transformations is applied before and after interpretation~\sx{two}.

%FIXME: Need to start with both problems
Some analyses may themselves make use of global variables, libraries, and other analyzable constructs.
As these will be part of the same execution context, \sys must note to avoid transforming and wrapping these constructs as part of the analysis.
% The analysis language is embedded in the source language, thus \sys makes use of the language's built-in evaluation primitives to interpret the \pc specification file.
Dialysis frameworks may also want to add analysis-specific keywords not provided by the language.
To achieve this, \sys wraps each analysis hook with a function whose body starts by defining the expected keywords.
The precise techniques for achieving this will be made clear in the next section~\sx{two}, after covering transformations;
  the key point to remember is that analyses are initially represented as source strings, similar to libraries.

@@

Program dialysis depends on a few features provided by the programming language.
In this section, we start by describing its requirements~\sx{reqs} and then reflect on some of its strengths and weaknesses~\sx{principles}.

\subsection{Applying \sys to Other Environments}
\label{reqs}

>>>>

@@

%for single author (just remove % characters)
\author{
{\rm Anonymous Author(s)}\\
\normalsize{Submission \#225, 12 pages}\\
% \normalsize{Additional Anonymized Material: \href{https://git.io/JvfCf}{https://git.io/JvfCf}.}
% {\rm Grigoris Ntousakis}\\
% Technical University of Crete
% \and
% {\rm Nikos Vasilakis}\\
% Massachusetts Institute of Technology
}

@@

To address these challenges, we propose a novel approach to dynamic analysis, termed \emph{dialysis}\footnote{
  A method of deconstruction into elements often for the purposes of removing waste products or altering piecewise components.
  From ancient Greek {\scriptsize $\delta\iota\acute{\alpha}$} (di\'{a}, ``inter-, through'') and {\scriptsize $\lambda\acute{\tilde{\upsilon}}\epsilon\iota\nu$} (lúein, ``to loosen'').
} and implemented in \sys.
Program dialysis is a general technique, applicable to any programming language, that enables dynamic fragmentation, analysis, and re-assembly of applications at the level of individual libraries. 
It operates during program execution, automating wrapping and transformation of the program's dependency graph, and allowing developers to extract meaningful insights with only a few lines of analysis-specific code
By operating at the granularity of libraries, dialysis has several benefits over prior work: %full-fledged dynamic analysis:
  (i) it allows bolting library dialysis itself as a library onto existing runtime environments with no dynamic analysis,
  (ii) it supports analysis expressions using the same language, tools, and abstractions as the host program language,
  (iii) it features significantly low runtime performance overheads, enabling the potential for toggling its use in production environments.

@@

To demonstrate its effectiveness, we evaluate \sys on the JavaScript ecosystem (>1.2M libraries~\cite{modulecounts}). % and unusually high code-reuse~\cite{npmstudy:19}. %, and a pressing need for usable dynamic analysis~\cite{}.
We develop a diverse set of analyses that target practical information about a program:
  an allow/deny security analysis,
  a profiling analysis showing bottlenecked modules,
  a synthesis-oriented analysis on input-output data, and
  an analysis enforcing a static union-based type system at runtime.
This set of analyses drives the design requirements for \sys, and highlights dialysis as a middle ground between coarse- and fine-grained analysis.
We evaluate \sys at three different levels:
  (i) synthetic micro-benchmarks that test certain aspects and confirm the correctness of our analyses in a controlled environment;
  (ii) single-module meso-benchmarks that allow comparison with dynamic analysis frameworks; and
  (iii) end-to-end full-application macro-benchmarks that show behavior of \sys on realistic workloads. 
\S\ref{bg}--\ref{eval} present our key contributions:
\begin{itemize}
\item \S\ref{bg} characterizes the shared needs of four case-study multi-module analyses whose needs remain mostly unmet by general-purpose analysis frameworks.
\item \S\ref{design} presents the design of the bolt-on module-oriented dynamic analysis~\sx{design}, which meets the requirements of the four case-study analyses.
\item \S\ref{impl} discusses our implementation, \sys, as a pluggable library for the JavaScript ecosystem, as well as the implementation of the four analyses.
\item \S\ref{eval} evaluates \sys showing it expresses insightful analyses succinctly, adds minimal overheads over the baseline runtime, and scales to hundreds of modules.
\end{itemize}

@@

A single application today often incorporates multiple libraries written and published by several different authors.
To make the difficulties of analyzing such library-overreliant more concrete, we describe several example analysis that are often needed by the authors of third-party libraries.
These examples illustrate key requirements for the design of a framework for analyzing applications at the boundaries of modules.
Before describing these examples, however, we offer a brief refresher on the abstractions and corresponding internals of module systems~\sx{bg1}.

@@

A library, package, or module---we use these terms interchangeably---is a development-time construct for encapsulating reusable functionality.
This functionality falls into two categories:
  it either (i) comes bundled with the language, possibly wrapping operating-system interfaces such as the file-system in a way that is system-agnostic and conforms to the language's conventions,
  or (ii) is provided by other developers sharing code others might find useful.
Fig.~\ref{mod} depicts the basic structure of a modern program, in which the \ttt{math} library provides a set of four elementary operations.

From a developer's perspective, \ttt{import}ing a library makes its functionality usable by the calling code. 
What this means is that some of the library's functionality is bound to a variable name that becomes available in the scope of the caller.
This is provided through a form of \ttt{export}ing, where the library developer expresses which values should become available to the importing code.
The definition of a value depends on the semantics of the language, but for now we can assume it's either a primitive value, a list of values, a function, or an object mapping string keys to values.
Internally, the library might import other libraries, cause side-effects to the file-system and the network, or even be implemented in multiple languages.
% , as shown on line \fixme{XX},
% closely coupled with the runtime
% and in some cases features its own mini-language, as is the case in Scheme and Standard ML.

From the language's perspective, the loading process is achieved in several steps. 
In compiled programming languages libraries might be used to enable separate compilation, in which case an additional linking phase connects the resulting object files.
Interpreted languages involve a somewhat convoluted process that combines loading, interpretation, and linking.
This process starts by locating the library in the file system or across the network,\footnote{
  Examples of run-time environments featuring network loading include V8 and deno, for executing JavaScript and TypeScript respectively.
}
by resolving relative or absolute identifiers.
% The library is assigned a unique identifier.
The content of the library is then read and wrapped in a way that resolves library-local names such as \ttt{\_\_name\_\_} in Python and \ttt{\_\_filename} in JavaScript to meaningful values.
The wrapper is then interpreted and evaluated using the language's interpreter, which might result to side-effects---for example, a \ttt{process.exit} in the library's top-level scope will exit the entire program.
Finally, the value returned bound to the \ttt{export}ed interface or returned from this interpretation (depending on the language) will be made available to the scope of code calling \ttt{import}.

There is significant variation, but a few features are common across many implementations.
A library cache maintains a mapping from library identifiers---often absolute paths---to returned \ttt{export} values.
The library cache serves a dual purpose:
  by avoiding to locate already loaded libraries, it improves performance and maintains the consistency of stateful libraries.
Recursive imports are handled in depth-first way, and if cyclical dependencies are possible they are resolved by pointing to the cache.
An increasingly common feature is to allow different versions of the same library to co-exist in a program, in order to avoid a choice between mutually exclusive options---a paradoxical situation known as ``dependency hell''.
As a result, a single \ttt{import} \ttt{lib} does not necessarily resolve to the same (version of the) library \ttt{lib} every time.
The dual of this situation is also possible, in which two different library names may resolve to the same identifier (in which case the second will be redirected to the cache).
These features complicate library-level analysis, especially in interpreted programming languages.

@@

\subsection{Motivating Examples}

Having reviewed the building blocks and underlying techniques that power modularity, we now turn to examples of dynamic analysis that today are difficult or require specialized solutions:
  (i) an allow/deny security analysis,
  (ii) a profiling analysis showing hot libraries,
  (iii) a synthesis-oriented analysis on input-output data, and
  (iv) an analysis enforcing a static union-based type system at runtime.
These examples illuminate key design requirements for \sys's implementation of module-level dynamic analysis.

\heading{Security Analysis}
The pervasive reliance on third-party libraries has led to an explosion of supply-chain attacks~\cite{long2015owasp, maass2016theory, snyk, lauinger2017thou}.
Both bugs and malicious code in imported libraries create attack vectors, exploitable long after libraries reach their end-users.
As library boundaries do not exist at runtime, libraries end up executing with no meaningful isolation or privilege separation guarantees between each other and the trusted portions of a program.
Popular libraries, depended upon by tens of thousands of other libraries or applications, allow vulnerabilities deep in the dependency graph to affect a great number of applications~\cite{leftpad, npmstudy:19}.
Discovered vulnerabilities are becoming harder to eradicate, as updates are fetched automatically~\cite{npmFailure} and module unpublishing is becoming a multi-step process to avoid breaking applications~\cite{npmUnpublish}.
Worst of all, leaked publishing tokens allow attackers to update packages with code that will eventually reach end-users via package updates~\cite{eslint1}.

As a concrete example, consider the recent event-stream incident~\cite{es1, es2}, in which a maintainer of a highly popular library inserted code for stealing Bitcoin wallet credentials from a program using that library.
As event-stream activated its malicious behavior only on production---\ie not during testing or development---it is critical to be able to toggle the behavior of the system
At the same time, it is not critical to analyze behavior \emph{within} the event-stream library itself:
  if any data exfiltration is happening, this will require calling out of the library and into the network---in event-stream's case, using the \ttt{fs} library to modify a different library and then use \ttt{http} from the second library.
Both \ttt{fs} and \ttt{http} are libraries part of the standard library and built into the runtime environment.
% The key issue underlying the \ttt{event-stream} attack is that any third-party fragment of an application has unrestricted access to the functionality available to the rest of application.

To address such problems, several recent proposals suggest analyzing third-party modules dynamically to identify malicious behavior~\cite{}.
% FIXME more about the policy, tracking arguments too
A simple ``allow-deny'' security analysis indicating the resources touched by that library would have revealed access to the and access .
Examples of interfaces outside the \ttt{http} and \ttt{fs} libraries include the ability to use global variables, import other libraries, and access the cache of the loaded modules---all of which are easily available to any third-party that is part of an application.

@@

\heading{Performance Diagnosis}
Diagnosing performance problems is a difficult task, exacerbated by the heavy use of third-party libraries.
Libraries are written by authors with different education backgrounds, quality standards, and, most importantly, needs:
  it's not unusual for a weekend project solving a local need to end up as a critical dependency among several open source projects~\cite{}.
Maintenance and rewriting can cause performance regressions between two versions of a library.
% FIXME: Garbage collection
Worse even, the fact that one library changes a dependency to a different implementation can cause severe performance pathologies to upstream projects---that is, while the interface remains the same due to an intermediate layer of abstraction, performance characteristics change dramatically~\cite{evhaus}.

As a concrete example, consider the \ttt{minimatch} library, a regular-expression-based file-matching utility susceptible to long delays because of pathological regular expressions that involve backtracking.
Pathological inputs reaching \ttt{minimatch}, even if benign, can cause significant performance degradation.
The source of this degradation can lie deep in the dependency chain of the application~\cite{crosby2003denial}, but also affect logically unrelated parts competing for the same resource (\ie CPU).

The research community has proposed several possible mitigations~\cite{}, all critically depending on detecting and attributing the slowdown to the bottlenecked component.
An analysis 
% A key observation is the semantic isomorphism between calling a function and passing a message
% This allows viewing a series of calls as a stream of messages.
% Module boundaries can be viewed as (virtual) queues of messages that await processing.
treating library invocation boundaries as message queues~\cite{scheme:98, duality:79}.
Overwhelming a module causes its ingress queue to grow.
At some point, the waiting time of newly-arrived messages becomes longer than sending messages to a library replica.
Profiling is accomplished by wrapping module interfaces with logic that generates a model of the current workload.
Each module boundary collects its own statistics based on a combination of recipes and instructions from the coordinator.
Profile generation can operate at a high resolution in time and space:
  (i) at every function call entering a module, and (ii) on thousands of modules across an application.

\heading{Invariant Discovery}
Extracting type invariants is helpful in a variety of ways---type safety is an important property and types are lightweight annotations that can be quickly and efficiently checked.
Dynamic analysis can be used to generate type assertions or invariants
For example
e.
For example, types identify program invariants to be preserved during code modifications, to generate marshalling and marshalling wrappers, or even to guide library synthesis and regeneration.
This is especially problematic in dynamic programming languages:
  in the absence of type signatures, there is not much one can say about a \ttt{http.request} object.

To make this concrete, consider the case of the \ttt{gRPC} library for serializing and de-serializing objects.
Given a ---say, a simple bignum library or a crypto---a developer has to first run the library manually, take note of the result, and then write a protocol buffer specification file declaring the type; %, common in distributed systems
if the type changes, because of a library version change or because of changes in the .

The static type system is defined as a variant of a simply-typed lambda calculus augmented with union types.
A simple approach would be to define a very simple type system that captures the type of a value by observing the execution of the program---after all, the types are dynamically checked!
The analysis could also capture union types, for cases where it observes that a variable is at times witnessed to hold values of different types---although a single program tends to make calls of the same type signature across its entire lifetime~\cite{daikon}.
The analysis could also do some type ``unpacking'' to deconstruct a type to its structural primitives---for example, noting that an object of type user is comprised of two strings (first and last name) and a number (age).

@@

\subsection{Design Goals}

We have briefly introduced four motivating analyses for extracting information about an application's dependencies.
While the challenges behind these analyses share several characteristics, today they remain largely unaddressed by dynamic analyses frameworks due to a combination of factors:
  these frameworks either require highly specialized solutions often outside the core language,
  do not leverage or offer semantic information at the level of module boundaries, or
  lead to a high (often impractical) performance overheads due to the high granularity of their analyses.
To summarize, these applications would appear to be served well by a system that:
\begin{itemize}
  \item \textbf{(G1)} Operates at the level of modules, leveraging both the semantics and performance potential that this level of granularity potentially offers.
  \item \textbf{(G2)} Does not require learning a new tool or language, but rather allows developers to express their analyses on the same language as the program.
  \item \textbf{(G3)} Can be implemented as a library that bolts onto an existing language runtime environment.
\end{itemize}

The next section describes program dialysis, a new program analysis technique that satisfies these goals, in a language-agnostic manner~\sx{design};
  the section following that describes a concrete implementation for the server-side JavaScript ecosystem~\sx{impl}.

@@

% FIXME: add user data
At a high level, the goal of program dialysis is to dismantle the program at the boundaries of third-party libraries, apply transformations that insert analysis-specific machinery, and then carefully assemble individual components to maintain the original semantics.
 In more detail:

@@

  \item \textbf{Dismantling:}
Dialysis starts by recursively dismantling a program into its dependencies. % ---pieces of software implement a computation or functionality.
This is achieved by re-wiring the language's \ttt{import} functionality to go through \sys, resulting in \sys walking the program's recursive dependency structure at runtime.
During this phase, \sys has to determine the granularity of the analysis (\eg top-level libraries, a specific library \etc) in order to apply transformations at the correct level and mapping provided analysis hooks to the corresponding libraries.

@@

  \item \textbf{Re-assembly}
Finally, dialysis re-assembles individual modified libraries back into the program's original structure.
The most important challenge during this phase the treatment of the library cache~\sx{bg1}:
  since a single library can now correspond to many different wrappers, each modified to capture a small fragment of the overall analysis, the cache needs to be augmented to ensure the right analysis fragment clicks at the right place during the re-assembly of the dependency tree.

@@

\begin{figure}[t]
\raggedleft 
\includegraphics[width=0.45\textwidth]{./figs/lya_base.pdf}
\caption{
  \textbf{Base transformation.}
  \textmd{
  The algorithm (simplified) is presented in functional style to simplify variable binding; types (object, list, function, and primitive), used for pattern matching, are shown in light {\color{cdb} \emph{turquoise}}~\cf{bt}. The meta-function $\alpha$ stands for the locations of analysis hooks.
  }
}
\label{fig:base}
\end{figure}

@@

When the dialysis starts along with the rest of the program, it first loads the analysis hooks provided by the developer. 
Among other things, \sys needs to determine which library boundaries are of interest and what the granularity of the analysis is going to be.
For the former, developers may have specified a subset of libraries whose boundaries are of interest or a subset of libraries that should \emph{not} be analyzed.
For the latter, it checks the constructs that---for example, whether the analysis includes global variables, library-local constructs, standard libraries \etc

It then dynamically replaces the implementation of\ttt{import}:
  rather than simply locating and loading a library, the function yields to \sys.

\sys checks the cache~\sx{three} to determine (i) if the library has already been loaded, and (ii) whether it has been loaded with the same analysis hooks.
If both are determined true, \sys retrieves the cached version of the library and returns the transformed \ttt{export}ed value.
If the library was loaded with a different analysis---say because there are different analyses applied to different parts of a dependency tree---\sys constructs the appropriate analysis and applies a transformation pass on a cached copy of the unmodified library~\sx{three}.
% \omit{---the common case---}
Otherwise, \sys first invokes the built-in library loader to locate the library.

The process of loading new libraries includes (i) a phase of reading the necessary files as source code and (ii) a phase of interpreting them, interspersed by applications of transformations.
Reading files returns a string representation of the code; interpretation uses the language's runtime evaluation primitives to convert the code to an in-memory object.
A series of transformations is applied before and after interpretation~\sx{two}.

Some analyses may themselves make use of global variables, libraries, and other analyzable constructs.
\sys must note not to include these constructs in the ones 
% The analysis language is embedded in the source language, thus \sys makes use of the language's built-in evaluation primitives to interpret the \pc specification file.
Dialysis frameworks may want to add analysis-specific keywords not provided by the language.
To achieve this, \fixme{we} wrap each analysis hook with a function whose body starts by defining the expected keywords.
The precise techniques for achieving this will be made clear in the next section~\sx{two}, after covering transformations;
  the key to remember is that analysis are loaded from disk as source files, similar to libraries.

@@

Library dialysis, as implemented in \sys, depends on a few features available in the programming language.
In this section we describe how to develop the same solution on other environments.
In the second part of this section, we reflect on some of the current limitations of the system.

\subsection{Applying to Other Environments}
\label{reqs}
